Corotating Dust Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-06-29 paper/ms.tex
update ms

Table~\ref{tab:thetable} lists the \ncpvsfound\ CQVs identified by our
search, along important physical and observational properties.
\ngoods\ objects demonstrate what we view as unambiguous
characteristics of the CQV phenomenon in at least one TESS sector, and
we refer to these as the ``gold sample''.  The remaining \nmaybes\ CQV
candidates were ambiguous (in our view), and their variability might
be caused by say, multiple starspot groups.  Additional data from TESS
or other instruments can help resolve their classification; in
Section~\ref{subsec:irexcess} below for instance we discuss a few
cases in this ambiguous sample that are probably dippers.

@@

A small number of objects at first glance seem reminiscent of
eclipsing binaries, for instance TIC~193831684 or TIC~5714469.  In the
few such cases, we believe that that are unlikely to be eclipsing
binaries due to additional coherent variations in the light curves
that are distinct from any binary phenomenology of which we are aware.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.9\textwidth]{TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3.pdf}
		\vspace{-0.45cm}
		\caption{
			Evolution of LP 12-502 ($P$=18.6\,h) at fixed period and
			epoch over three years. 
			Each panel shows one (stacked) TESS orbit; small text denotes relative cycle number.
			There are 200 binned black points per cycle.
			The TESS pointing law dictates time gaps; larger gaps tend to
			yield larger shape changes.
			The dips usually evolve over tens to hundreds of cycles.
			However cycles 1233-1264 show a dip that ``switched'' from a depth
			and duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than
			one cycle.
		}
		\label{fig:lp}
	\end{center}

@@

\paragraph{Quasiperiodicity}
A periodic signal does not modulate; the CQVs are {\it quasi}periodic.
This is a qualitative departure from
the ``persistent'' {\it vs.} ``transient'' flux dip distinction from 
\citet{2017AJ....153..152S}.  While the dips can appear persistent
over timescales of even up to 100 cycles, our view is that all the CQV
dips seem to be transient over timescales of more than 1000 cycles
(Figure~\ref{fig:evoln}).

With that said, one might expect a truly quasiperiodic process to be
able to explore all phase angles with equal weight.  LP 12-502, and
many other CQVs, have preferred phases.  For LP 12-502 for instance,
all of the dips happen over a fixed phase duration of two thirds of
the period.  Phases between $\{0.45,0.8\}$ are ``out of limits'' for
any dipping material.  We interpret this as evidence
either that {\it a)} some aspect the stellar magnetic field is
strongly asymmetric, and can generate and hold stellar prominences at
corotation, but only over two thirds of the great circle,
or {\it b)} there is a physical structure -- for instance a
disintegrating planetesimal swarm -- that is distributed over an arc
of about 240$^\circ$.

@@

{\bf author contribution statement goes here}
L.G.B.~and R.~J. conceived the project and executed the
dip-based and Fourier-based searches, respectively.
L.G.B.~drafted the initial manuscript, and performed the cluster
membership analysis.
S.~R. and R.~J. vetted the results from the Fourier search.
L.A.H.~contributed to project design.
All authors assisted in manuscript revision.

>>>>

Table~\ref{tab:thetable} lists the \ncpvsfound\ CQVs identified by our
search, along important physical and observational properties.
\ngoods\ objects demonstrate what we view as unambiguous
characteristics of the CQV phenomenon in at least one TESS sector, and
we refer to these as the ``gold sample''.  The remaining \nmaybes\ CQV
candidates were ambiguous (in our view), and their variability might
be caused by say, multiple starspot groups.  Additional data from TESS
or other instruments can help resolve their classification; in
Section~\ref{subsec:irexcess} below for instance we discuss a few
cases in this ambiguous sample that after additional analysis were
clarified as dippers.  We also emphasize that our initial
classifications were based on whether {\it any} TESS sectors showed
evidence for the CQV phenomenon.

@@

A small number of objects at first glance seem reminiscent of
eclipsing binaries, such as TIC~193831684 or TIC~5714469.  In the
few such cases, we believe that that are unlikely to be eclipsing
binaries due to additional coherent variations in the light curves
that are distinct from any binary phenomenology of which we are aware.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.9\textwidth]{TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3.pdf}
		\vspace{-0.45cm}
		\caption{
			Evolution of LP 12-502 ($P$=18.6\,h) at fixed period and
			epoch over three years. 
			Each panel shows one (stacked) TESS orbit; small text denotes relative cycle number.
			There are 200 binned black points per cycle.
			The TESS pointing law dictates time gaps; larger gaps tend to
			yield larger shape changes.
			The dips usually evolve over tens to hundreds of cycles.
			However cycles 1233-1264 show a dip that ``switched'' from a depth
			and duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than
			one cycle (see Figure~\ref{fig:lplc}).
		}
		\label{fig:lp}
	\end{center}

@@

\paragraph{Extremes}
The closest CQV in our catalog is DG~CVn (TIC~368129164;
$d$$=$18\,pc), which is a likely member of AB Dor.  To our knowledge,
this manuscript is the first time that it has been noted as a CQV.

The shortest period belongs to TIC~201789285, at 3.64\,hr.
The longest period belongs to TIC~405910546, at 37.9\,hr.  If
that source turns out to be an eclipsing binary, then the next-longest
would be TIC~193831684 (31.0\,hr).

The lowest mass ($\approx 0.12$\,M$_\odot$) belongs to TIC~50745567.
There are a number of other similar very low mass stars, which
suggests the phenomenon may extend into the brown dwarf regime.

The three brightest CQVs in Table are DG~CVn ($T$=9.3), TIC~405754448
($T$=9.6), and TIC~167664935 ($T$=10.3).

\paragraph{Quasiperiodicity}
A periodic signal does not modulate; the CQVs are {\it quasi}periodic.
This is a qualitative departure from
the ``persistent'' {\it vs.} ``transient'' flux dip distinction from 
\citet{2017AJ....153..152S}.  While the dips can appear persistent
over timescales of even up to 100 cycles, all the CQV dips seem to be
transient over timescales of more than 1000 cycles
(Figure~\ref{fig:evoln}).
The distinction is not therefore particularly meaningful.

With that said, one might expect a truly quasiperiodic process to be
able to explore all phase angles with equal weight.  LP 12-502, and
many other CQVs, seem to have preferred phases.  For LP 12-502,
all of the dips happen over a fixed phase duration of two thirds of
the period.  Phases over the other third are ``out of limits'' for
any dipping material.  We interpret this as evidence
either that {\it a)} some aspect the stellar magnetic field is
strongly asymmetric, and can generate and hold extrinsic material at
corotation, but only over two thirds of the great circle,
or {\it b)} there is a physical structure -- for instance a
disintegrating planetesimal swarm -- that is distributed over an arc
of the same angular extent (240$^\circ$).

@@

{\bf author contribution statement goes here}
L.G.B.~and R.~J. conceived the project and executed the
dip-based and Fourier-based searches, respectively.
L.G.B.~drafted the initial manuscript, and performed the cluster
membership analysis.
S.~R. and R.~J. vetted the results from the Fourier search.
L.A.H.~advised on project scope and experiment design.
All authors assisted in manuscript revision.
